Who does big team science?

### 2023-03-23 manuscript_scopus.Rmd
all the updates

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(flextable)
library(wordcloud2)
library(htmlwidgets)
library(webshot)
library(figpatch)
```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip")

@@

***Institution***. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Sub-Region for
analyses.

@@

The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences. The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X.

@@

@@

```{r}
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(count = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary")

health_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

@@

physical_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

@@

life_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

@@

social_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(ASJC, count))

@@

ggplot(graph_data, aes(label, estimate)) + 
  geom_point() +
  geom_pointrange(aes(ymin = low, ymax = high)) +
  theme_classic() + 
  facet_wrap(~type) + 
  geom_hline(yintercept = 0) + 
  coord_flip() + 
  xlab("Subject Area") + 
  ylab("")
```

@@

```{r}
ggplot(DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
       aes(Decade, `count(affiliation_ids)`)) + 
  #geom_point() + 
  geom_violin() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  ylab("Number of Affiliations") + 
  xlab("Decade")
```

@@

DF$geo_country <- DF$geo_country %>% 
  group_by(affiliation_tag_country) %>% 
  summarize(count = sum(count))

@@

# map of binned data 
bin_country <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_manual(name = "Sample Size",
                    values = c( "black", "#323232", "#646464","#969696","#c8c8c8"))

@@

tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "white", place = "centre",
                    size = 15, grow = FALSE) +  
  scale_fill_manual(name = "Sample Size",
                    values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

@@

@@

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab("Effect Size") + 
  scale_size_continuous(name = "Num Authors")

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab("Effect Size") + 
  scale_size_continuous(name = "Num Authors")

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab("Effect Size") + 
  scale_size_continuous(name = "Num Authors")

@@

```{r author-gpe-figure, include = TRUE}
small_author + #theme(legend.position = "none") + 
medium_author + #theme(legend.position = "none") + 
large_author + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

@@

```{r effect-gpe-figure, include = TRUE}
small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

>>>>

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(flextable)
library(wordcloud2)
library(htmlwidgets)
library(webshot)
library(figpatch)

strip_labels <- expression(
  "M Coefficient" = b[M],
  "SD Coefficient" = b[SD],
  "Effect Size" = R^2
)

label_expressions <- function(values) {
  stopifnot(is.expression(values))
  as_labeller(function(x) {
    if (is.null(names(values))) {
      x <- seq_along(x)
      if (length(x)!=length(values)) warning(paste0("Number of labels(", 
        length(values), ") does not match number of values (", length(x), ")"))
    }
    as.list(values[x])
  }, default=identity)
}

```

```{r data, include = FALSE}
# things to import
var_list <- c("author_time", "career_time", "geo_country", "inst_time", 
              "keywords", "large_first_gp", "large_other_gp", "medium_first_gp", 
              "medium_other_gp", "normal_pub_type", "pub_time_count", 
              "pub_time_subject", "pub_types", "small_first_gp", "small_other_gp",
              "snip", "ASJC_codes", "snip_all")

@@

***Institution and Geopolitical Region ***. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Region, Sub-Region,  or smaller clusters for
analyses.

@@

The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences. The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X. For comparison, the SNIP descriptive statistics for all papers is shown in Table X.

Big-Team Science SNIP

@@

All Journal Articles SNIP

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip_all %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

```{r}
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(count = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))

health_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0)

@@

physical_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0, 
             size = 1.5)

@@

life_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0)

@@

social_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0, 
             size = .2)

@@

ggplot(graph_data, aes(label, estimate)) + 
  geom_point() +
  geom_pointrange(aes(ymin = low, ymax = high)) +
  theme_classic() + 
  facet_wrap(~type, labeller  = labeller(type = label_expressions(strip_labels))) + 
  geom_hline(yintercept = 0) + 
  coord_flip() + 
  xlab("Subject Area") + 
  ylab("")
```

@@

```{r}
DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100

ggplot(DF$inst_time %>% 
         filter(SubjectArea != "Multidisciplinary") %>% 
         mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))), 
       aes(Decade, `normalized`)) + 
  #geom_point() + 
  geom_violin() + 
  theme_classic() + 
  facet_wrap(~SubjectArea) + 
  ylab("Percent of Unique Affiliations") + 
  xlab("Decade")
```

@@

DF$geo_country <- DF$geo_country %>% 
  group_by(affiliation_tag_country) %>% 
  summarize(count = sum(count),
            count_all = sum(all_count))

@@

DF$geo_country$count_binned <- factor(DF$geo_country$count_binned, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000+"))

# map of binned data 
bin_country <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")

@@

tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

@@

```{r geo-map-all}
# make a map on a continuous scale
ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_all), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_distiller(name = "Sample Size",
                       palette = "Greys",
                       direction = 1,
                       na.value = "white")

ggsave("figure/continuous_country_all.png")

# maybe try binning
DF$geo_country$count_binned_all <- if_else(
  DF$geo_country$count_all >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
        "< 100"
      )
    )
  )
)

DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
                                   levels = unique(DF$geo_country$count_binned_all))

DF$geo_country$count_binned_all <- factor(DF$geo_country$count_binned_all, 
                                      levels = c("< 100", 
                                                 "100-999", 
                                                 "1,000-4,999", 
                                                 "5,000-9,999", 
                                                 "10,000+"))

# map of binned data 
bin_country_all <- ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_binned_all), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  # scale_fill_manual(name = "Sample Size",
  #                   values = c( "black", "#323232", "#646464","#969696","#c8c8c8")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")

bin_country_all

ggsave("figure/binned_country_all.png", bin_country_all)

tree_all <- ggplot(DF$geo_country, aes(area = count_all, fill = count_binned_all,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

tree_all

ggsave("figure/treemap_all.png", tree_all)
```

@@

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

```{r author-gpe-figure, include = TRUE}
small_author + ggtitle("10-49 Authors") + #theme(legend.position = "none") +
medium_author + ggtitle("50-99 Authors") + #theme(legend.position = "none") + 
large_author + ggtitle("100 + Authors") + #theme(legend.position = "none") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

@@

```{r effect-gpe-figure, include = TRUE}
small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("10-49 Authors") + 
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("50-99 Authors") +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("100 + Authors") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")
